A Cross-Benchmark Comparison of 87 Learning to Rank Methods

### 2014-09-15 paper/IPM/paper.tex
title page
apa + png->jpg
2->1 column

\documentclass[preprint]{elsarticle}
\usepackage{booktabs}
\usepackage{multicol}
\usepackage{longtable}
\usepackage{dblfloatfix}
\usepackage{fixltx2e}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage{float}
\renewcommand{\dblfloatpagefraction}{2.0}
\usepackage{array}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\usepackage{balance}

@@

\begin{document}
\begin{frontmatter}
\title{A Cross-Benchmark Comparison of 87 Learning to Rank Methods}

\author[avanade,ut]{Niek Tax\corref{cor}\fnref{fn}}
\ead{niek.tax@avanade.com}

\author[avanade]{Sander Bockting}
\ead{sander.bockting@avanade.com}

\author[ut]{Djoerd Hiemstra}
\ead{d.hiemstra@utwente.nl}

\cortext[cor]{Corresponding author}
\fntext[fn]{Author is affiliated with the University of Twente, but this paper written during his time at Avanade Netherlands B.V.}

\address[avanade]{Avanade Netherlands B.V., Versterkerstraat 6,
1322AP Almere, the Netherlands}
\address[ut]{University of Twente, P.O. Box 217, 7500AE Enschede,
the Netherlands}
\begin{abstract}
Learning to rank is an increasingly important scientific field that comprises the use of machine learning for the ranking task. New learning to rank methods are generally evaluated on benchmark test collections. However, comparison of learning to rank methods based on evaluation results is hindered by non-existence of a standard set of evaluation benchmark collections. In this paper we propose a way to compare learning to rank methods based on a sparse set of evaluation results on a set of benchmark datasets. Our comparison methodology consists of two components: 1) Normalized Winning Number, which gives insight in the ranking accuracy of the learning to rank method, and 2) Ideal Winning Number, which gives insight in the degree of certainty concerning its ranking accuracy. Evaluation results of 87 learning to rank methods on 20 well-known benchmark datasets are collected through a structured literature search. ListNet, SmoothRank, FenchelRank, FSMRank, LRUF and LARF are the best performing learning to rank methods in increasing order of Normalized Winning Number and decreasing order of Ideal Winning Number.
\end{abstract}
\begin{keyword}
Learning to rank \sep Information retrieval \sep Evaluation metric
\end{keyword}
\end{frontmatter}

@@

\subsection{NDCG@3}
\begin{figure}
\centering
\includegraphics[scale=0.19]{gfx/ndcg3_winnum}
\caption{NDCG@3 comparison of 87 learning to rank methods}
\label{fig:normalized_winning_number_ndcg3}
\end{figure}
Figure \ref{fig:normalized_winning_number_ndcg3} shows the NWN of learning to rank methods based on NDCG@3 results. LambdaNeuralRank and CoList both acquired a NWN score of 1.0 by beating all other algorithms on one dataset, with LambdaNeuralRank winning on the AOL dataset and CoList winning on Yahoo Set 2. LARF and LRUF scored very high scores of near 1.0 on three of the LETOR 3.0 datasets, which results in more certainty on these methods' performance because they are validated on three datasets that additionally are more relevant than AOL and Yahoo Set 2 (number of evaluation results for LETOR 3.0 are higher than those for AOL and Yahoo set 2). FenchelRank, OWPC, SmoothRank, DCMP and ListNet are ordered decreasingly by NWN and at the same time increasingly in number of datasets that they are evaluated on, resulting in a higher degree of certainty on the accuracy of the algorithms.\\

@@

\subsection{NDCG@5}
\begin{figure}
\includegraphics[scale=0.19]{gfx/ndcg5_winnum}
\caption{NDCG@5 comparison of 87 learning to rank methods}
\label{fig:normalized_winning_number_ndcg5}
\end{figure}
Figure \ref{fig:normalized_winning_number_ndcg5} shows the NWN of learning to rank methods based on NDCG@5 results. LambdaNeuralRank again beat all other methods solely with results on the AOL dataset scoring a NWN of 1.0. LARF, LRUF, FenchelRank, SmoothRank, DCMP and ListNet are from left to right evaluated on an increasing number of datasets, but score decreasingly well in terms of NWN. These results are highly in agreement with the NDCG@3 comparison. The only modification compared to the NDCG@3 comparison being that OWPC did show to be a method for which there were no methods performing better on both axes in the NDCG@5 comparison, but not in the @3 comparison. Like in the NDCG@3 comparison, SmoothRank and ListNet can be regarded as most reliable results because the evaluation measurements for these methods are based on LETOR official baselines.

\subsection{NDCG@10}
\begin{figure}
\centering
\includegraphics[scale=0.19]{gfx/ndcg10_winnum}
\caption{NDCG@10 comparison of 87 learning to rank methods}
\label{fig:normalized_winning_number_ndcg10}
\end{figure}

@@

\subsection{MAP}
\begin{figure}
\centering
\includegraphics[scale=0.19]{gfx/map_winnum}
\caption{MAP comparison of 87 learning to rank methods}
\label{fig:normalized_winning_number_map}
\end{figure}
Figure \ref{fig:normalized_winning_number_map} shows the NWN of learning to rank methods based on MAP results. Comparisons on the NDCG metrics where highly in agreement on the best performing algorithms, MAP-based NWN results show different results. RankDE scores a NWN of 1.0 on one dataset, which is achieved by obtaining highest MAP-score on the LETOR 2.0 TD2003 which has many evaluation results are evaluated.\\

@@

\subsection{Cross-Metric}
\begin{figure}
\centering
\includegraphics[scale=0.21]{gfx/combined_normalized_winnum}
\caption{Cross-benchmark comparison of 87 learning to rank methods}
\label{fig:normalized_winning_number_all}
\end{figure}
Figure \ref{fig:normalized_winning_number_all} shows the NWN as function of IWN for the methods described in Table \ref{tab:ltr_methods_used}. The cross-metric comparison is based on the NDCG@$\{3,5,10\}$ and MAP comparisons combined, which justifies analysing the comparison more thoroughly. Figure \ref{fig:normalized_winning_number_all} labels the algorithms with no other algorithm having a higher value on both the horizontal axis and vertical axis, but also labels the algorithms with exactly one algorithm having a higher value on both axes with smaller font size. In addition, Linear Regression and the ranking method of simply sorting on the best single feature are labelled as baselines.\\

@@

\bibliographystyle{apa}
\bibliography{Bibliography}

@@

\begin{tabular}{lll|lll}\toprule
Method & Described in & Evaluated in & Method & Described in & Evaluated in\\

@@

AdaRank-MAP & \cite{Xu2007} & L2, L3, L4 & ListMLE & \cite{Xia2008} & \cite{Lin2010, Lin2011, Gao2014} \\
AdaRank-NDCG & \cite{Xu2007} & L2, L3, L4,  \cite{Busa-Fekete2013,Tan2013} & ListNet & \cite{Cao2007} & L2, L3, L4 \\ 
ADMM & \cite{Duh2011} & \cite{Duh2011} & ListReg & \cite{Wu2011} & \cite{Wu2011} \\ 
ApproxAP & \cite{Qin2010b} & \cite{Qin2010b} & LRUF & \cite{Torkestani2012b} & \cite{Torkestani2012b} \\ 
ApproxNDCG & \cite{Qin2010b} & \cite{Qin2010b} & MCP & \cite{Laporte2013} & \cite{Laporte2013} \\ 
BagBoo & \cite{Pavlov2010} & \cite{Ganjisaffar2011c} & MHR & \cite{Qin2007} & L2 \\ 
Best Single Feature &  & \cite{Gomes2013} &  MultiStageBoost & \cite{Kao2013} & \cite{Kao2013} \\ 
BL-MART & \cite{Ganjisaffar2011c} & \cite{Ganjisaffar2011c} &  NewLoss & \cite{Peng2010} & \cite{Peng2010} \\ 
BoltzRank-Single & \cite{Volkovs2009} & \cite{Volkovs2009, Volkovs2013} & OWPC & \cite{Usunier2009} & \cite{Usunier2009} \\ 
BoltzRank-Pair & \cite{Volkovs2009} & \cite{Volkovs2009, Ganjisaffar2011c, Volkovs2013} & PERF-MAP & \cite{Pan2011} & \cite{Torkestani2012b} \\ 
BT & \cite{Zhou2008} & \cite{Zhou2008} & PermuRank & \cite{Xu2008} & \cite{Xu2008} \\ 
C-CRF & \cite{Qin2008b} & \cite{Qin2008b} & Q.D.KNN & \cite{Geng2008} & \cite{Wang2013} \\ 
CA & \cite{Metzler2007} & \cite{Busa-Fekete2013,Tan2013} & RandomForest & \cite{Gomes2013} & \cite{Gomes2013} \\ 
CCRank & \cite{Wang2011c} & \cite{Wang2011c} & Rank-PMBGP & \cite{Sato2013} & \cite{Sato2013} \\ 
CoList & \cite{Gao2014} & \cite{Gao2014} & RankAggNDCG & \cite{Wang2013} & \cite{Wang2013} \\
Consistent-RankCosine & \cite{Ravikumar2011} & \cite{Tan2013} & RankBoost & \cite{Freund2003} & L2, L3, L4, \cite{Busa-Fekete2013, Alcantara2010, Sato2013} \\
DCMP & \cite{Renjifo2012}  & \cite{Renjifo2012}  & RankBoost (Kernel-PCA) & \cite{Duh2008} & \cite{Duh2008, Sato2013} \\
DirectRank & \cite{Tan2013} & \cite{Tan2013} & RankBoost (SVD) & \cite{Lin2009} & \cite{Lin2009} \\
EnergyNDCG & \cite{Freno2011} & \cite{Freno2011} & RankCSA & \cite{He2010} & \cite{He2010} \\
FBPCRank & \cite{Lai2011} & \cite{Lai2011} & RankDE & \cite{Bollegala2011} & \cite{Sato2013} \\
FenchelRank & \cite{Lai2013} & \cite{Lai2013, Lai2013b, Laporte2013} & RankELM (pairwise) & \cite{Zong2013} & \cite{Zong2013} \\ 
FocusedBoost & \cite{Niu2012} & \cite{Niu2012} &  RankELM (pointwise) & \cite{Zong2013} & \cite{Zong2013} \\ 
FocusedNet & \cite{Niu2012} & \cite{Niu2012} & RankMGP & \cite{Lin2012} & \cite{Lin2012} \\ 
FocusedSVM & \cite{Niu2012} & \cite{Niu2012} & RankNet & \cite{Burges2005} & \cite{Busa-Fekete2013, Papini2012, Niu2012} \\ 
FP-Rank & \cite{Song2013} & \cite{Song2013} & RankRLS & \cite{Pahikkala2009} & \cite{Pahikkala2010} \\ 
FRank & \cite{Tsai2007} & L2, L3, \cite{Wang2012} & RankSVM & \cite{Herbrich1999, Joachims2002} & L2, L3, \cite{Busa-Fekete2013, Freno2011, He2010, Alcantara2010, Papini2012} \\ 
FSMRank & \cite{Lai2013c} & \cite{Lai2013c,Laporte2013} & RankSVM-Primal &  & L3, \cite{Lai2011} \\ 
FSM$^{SVM}$ & \cite{Lai2013c} & \cite{Lai2013c} & RankSVM-Struct &  & L3, L4 \\
GAS-E & \cite{Geng2007} & \cite{Lai2013c} & RCP & \cite{Elsas2008} & \cite{Elsas2008} \\ 
GP & \cite{DeAlmeida2007} & \cite{Alcantara2010} & RE-QR & \cite{Veloso2010} & \cite{Veloso2010} \\
GPRank & \cite{Silva2009} & \cite{Torkestani2012} & REG-SHF-SDCG & \cite{Wu2009} & \cite{Wu2009} \\  
GRankRLS & \cite{Pahikkala2010} & \cite{Pahikkala2010} & Ridge Regression & \cite{Cossock2006} & L3 \\
GroupCE & \cite{Lin2011} & \cite{Lin2011} & RSRank & \cite{Sun2009} & \cite{Lai2013} \\ 
GroupMLE & \cite{Lin2010} & \cite{Lin2011} & SmoothGrad & \cite{Le2007} & \cite{Tan2013} \\ 
IntervalRank & \cite{Moon2010} & \cite{Moon2010, Freno2011} & SmoothRank & \cite{Chapelle2010} & L3, \cite{Chapelle2010} \\
IPRank & \cite{Wang2009b} & \cite{Wang2009b, Torkestani2012} & SoftRank & \cite{Taylor2008, Guiver2008} & \cite{Qin2010b} \\ 
KeepRank & \cite{Chen2009} & \cite{Chen2009} & SortNet & \cite{Rigutini2008} & \cite{Rigutini2008,Freno2011, Papini2012} \\
KL-CRF & \cite{Volkovs2011} & \cite{Volkovs2011} & SparseRank & \cite{Lai2013b} & \cite{Lai2013b} \\ 
LAC-MR-OR & \cite{Veloso2008} & \cite{Veloso2008, Alcantara2010} & SVM$^{MAP}$ & \cite{Yue2007} & L3, \cite{Wang2012, Xu2008, Niu2012} \\ 
LambdaMART & \cite{Burges2010} & \cite{Asadi2013a, Ganjisaffar2011c} &SwarmRank & \cite{Diaz-Aviles2009} & \cite{Sato2013} \\ 
LambdaNeuralRank & \cite{Papini2012} & \cite{Papini2012} & TGRank & \cite{Lai2013} & \cite{Lai2013} \\ 
LambdaRank & \cite{Burges2006} & \cite{Papini2012, Tan2013} & TM & \cite{Zhou2008} & \cite{Zhou2008, Papini2012, Tan2013} \\ 
LARF & \cite{Torkestani2012} & \cite{Torkestani2012} &  VFLR & \cite{Cai2012} & \cite{Cai2012} \\
Linear Regression & \cite{Cossock2006} & L3, \cite{Wang2012, Volkovs2011} & & & \\

>>>>

\documentclass[english, authoryear, preprint]{elsarticle}
\usepackage{booktabs}
\usepackage{multicol}
\usepackage{longtable}
\usepackage{dblfloatfix}
\usepackage{apalike}
\usepackage{fixltx2e}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage{float}
\renewcommand{\dblfloatpagefraction}{2.0}
\usepackage{array}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\usepackage{balance}

@@

\begin{document}
\begin{frontmatter}
\title{A Cross-Benchmark Comparison of 87 Learning to Rank Methods}
\author[avanade,ut]{Niek Tax\corref{cor}\fnref{fn}}
\ead{niek.tax@avanade.com}
\author[avanade]{Sander Bockting}
\ead{sander.bockting@avanade.com}
\author[ut]{Djoerd Hiemstra}
\ead{d.hiemstra@utwente.nl}
\cortext[cor]{Corresponding Author: Niek Tax, Avanade Netherlands B.V., Versterkerstraat 6,
1322AP Almere, the Netherlands; Email, niek.tax@avanade.com; Phone, +31634085760}
\fntext[fn]{Author is affiliated with the University of Twente, but this paper written during his time at Avanade Netherlands B.V.}
\address[avanade]{Avanade Netherlands B.V., Versterkerstraat 6,
1322AP Almere, the Netherlands}
\address[ut]{University of Twente, P.O. Box 217, 7500AE Enschede,
the Netherlands}
\begin{abstract}
Learning to rank is an increasingly important scientific field that comprises the use of machine learning for the ranking task. New learning to rank methods are generally evaluated on benchmark test collections. However, comparison of learning to rank methods based on evaluation results is hindered by non-existence of a standard set of evaluation benchmark collections. In this paper we propose a way to compare learning to rank methods based on a sparse set of evaluation results on a set of benchmark datasets. Our comparison methodology consists of two components: 1) Normalized Winning Number, which gives insight in the ranking accuracy of the learning to rank method, and 2) Ideal Winning Number, which gives insight in the degree of certainty concerning its ranking accuracy. Evaluation results of 87 learning to rank methods on 20 well-known benchmark datasets are collected through a structured literature search. ListNet, SmoothRank, FenchelRank, FSMRank, LRUF and LARF are the best performing learning to rank methods in increasing order of Normalized Winning Number and decreasing order of Ideal Winning Number.
\end{abstract}
\begin{keyword}
Learning to rank \sep Information retrieval \sep Evaluation metric
\end{keyword}
\end{frontmatter}

@@

\subsection{NDCG@3}
\begin{figure}
\centering
\includegraphics[scale=0.26]{gfx/ndcg3_winnum}
\caption{NDCG@3 comparison of 87 learning to rank methods}
\label{fig:normalized_winning_number_ndcg3}
\end{figure}
Figure \ref{fig:normalized_winning_number_ndcg3} shows the NWN of learning to rank methods based on NDCG@3 results. LambdaNeuralRank and CoList both acquired a NWN score of 1.0 by beating all other algorithms on one dataset, with LambdaNeuralRank winning on the AOL dataset and CoList winning on Yahoo Set 2. LARF and LRUF scored very high scores of near 1.0 on three of the LETOR 3.0 datasets, which results in more certainty on these methods' performance because they are validated on three datasets that additionally are more relevant than AOL and Yahoo Set 2 (number of evaluation results for LETOR 3.0 are higher than those for AOL and Yahoo set 2). FenchelRank, OWPC, SmoothRank, DCMP and ListNet are ordered decreasingly by NWN and at the same time increasingly in number of datasets that they are evaluated on, resulting in a higher degree of certainty on the accuracy of the algorithms.\\

@@

\subsection{NDCG@5}
\begin{figure}
\centering
\includegraphics[scale=0.26]{gfx/ndcg5_winnum}
\caption{NDCG@5 comparison of 87 learning to rank methods}
\label{fig:normalized_winning_number_ndcg5}
\end{figure}
Figure \ref{fig:normalized_winning_number_ndcg5} shows the NWN of learning to rank methods based on NDCG@5 results. LambdaNeuralRank again beat all other methods solely with results on the AOL dataset scoring a NWN of 1.0. LARF, LRUF, FenchelRank, SmoothRank, DCMP and ListNet are from left to right evaluated on an increasing number of datasets, but score decreasingly well in terms of NWN. These results are highly in agreement with the NDCG@3 comparison. The only modification compared to the NDCG@3 comparison being that OWPC did show to be a method for which there were no methods performing better on both axes in the NDCG@5 comparison, but not in the @3 comparison. Like in the NDCG@3 comparison, SmoothRank and ListNet can be regarded as most reliable results because the evaluation measurements for these methods are based on LETOR official baselines.

\subsection{NDCG@10}
\begin{figure}
\centering
\includegraphics[scale=0.26]{gfx/ndcg10_winnum}
\caption{NDCG@10 comparison of 87 learning to rank methods}
\label{fig:normalized_winning_number_ndcg10}
\end{figure}

@@

\subsection{MAP}
\begin{figure}
\centering
\includegraphics[scale=0.26]{gfx/map_winnum}
\caption{MAP comparison of 87 learning to rank methods}
\label{fig:normalized_winning_number_map}
\end{figure}
Figure \ref{fig:normalized_winning_number_map} shows the NWN of learning to rank methods based on MAP results. Comparisons on the NDCG metrics where highly in agreement on the best performing algorithms, MAP-based NWN results show different results. RankDE scores a NWN of 1.0 on one dataset, which is achieved by obtaining highest MAP-score on the LETOR 2.0 TD2003 which has many evaluation results are evaluated.\\

@@

\subsection{Cross-Metric}
\begin{figure}
\centering
\includegraphics[scale=0.28]{gfx/combined_normalized_winnum}
\caption{Cross-benchmark comparison of 87 learning to rank methods}
\label{fig:normalized_winning_number_all}
\end{figure}
Figure \ref{fig:normalized_winning_number_all} shows the NWN as function of IWN for the methods described in Table \ref{tab:ltr_methods_used}. The cross-metric comparison is based on the NDCG@$\{3,5,10\}$ and MAP comparisons combined, which justifies analysing the comparison more thoroughly. Figure \ref{fig:normalized_winning_number_all} labels the algorithms with no other algorithm having a higher value on both the horizontal axis and vertical axis, but also labels the algorithms with exactly one algorithm having a higher value on both axes with smaller font size. In addition, Linear Regression and the ranking method of simply sorting on the best single feature are labelled as baselines.\\

@@

\bibliographystyle{apalike}
\bibliography{Bibliography}

@@

\begin{tabular}{lll}\toprule
Method & Described in & Evaluated in\\

@@

AdaRank-MAP & \cite{Xu2007} & L2, L3, L4 \\
AdaRank-NDCG & \cite{Xu2007} & L2, L3, L4,  \cite{Busa-Fekete2013,Tan2013} \\ 
ADMM & \cite{Duh2011} & \cite{Duh2011} \\ 
ApproxAP & \cite{Qin2010b} & \cite{Qin2010b} \\ 
ApproxNDCG & \cite{Qin2010b} & \cite{Qin2010b} \\ 
BagBoo & \cite{Pavlov2010} & \cite{Ganjisaffar2011c} \\ 
Best Single Feature &  & \cite{Gomes2013} \\ 
BL-MART & \cite{Ganjisaffar2011c} & \cite{Ganjisaffar2011c} \\ 
BoltzRank-Single & \cite{Volkovs2009} & \cite{Volkovs2009, Volkovs2013} \\ 
BoltzRank-Pair & \cite{Volkovs2009} & \cite{Volkovs2009, Ganjisaffar2011c, Volkovs2013} \\ 
BT & \cite{Zhou2008} & \cite{Zhou2008} \\ 
C-CRF & \cite{Qin2008b} & \cite{Qin2008b} \\ 
CA & \cite{Metzler2007} & \cite{Busa-Fekete2013,Tan2013} \\ 
CCRank & \cite{Wang2011c} & \cite{Wang2011c} \\ 
CoList & \cite{Gao2014} & \cite{Gao2014} \\
Consistent-RankCosine & \cite{Ravikumar2011} & \cite{Tan2013} \\
DCMP & \cite{Renjifo2012}  & \cite{Renjifo2012}  \\
DirectRank & \cite{Tan2013} & \cite{Tan2013} \\
EnergyNDCG & \cite{Freno2011} & \cite{Freno2011} \\
FBPCRank & \cite{Lai2011} & \cite{Lai2011} \\
FenchelRank & \cite{Lai2013} & \cite{Lai2013, Lai2013b, Laporte2013} \\ 
FocusedBoost & \cite{Niu2012} & \cite{Niu2012} \\ 
FocusedNet & \cite{Niu2012} & \cite{Niu2012} \\ 
FocusedSVM & \cite{Niu2012} & \cite{Niu2012} \\ 
FP-Rank & \cite{Song2013} & \cite{Song2013} \\ 
FRank & \cite{Tsai2007} & L2, L3, \cite{Wang2012} \\ 
FSMRank & \cite{Lai2013c} & \cite{Lai2013c,Laporte2013} \\ 
FSM$^{SVM}$ & \cite{Lai2013c} & \cite{Lai2013c} \\
GAS-E & \cite{Geng2007} & \cite{Lai2013c} \\ 
GP & \cite{DeAlmeida2007} & \cite{Alcantara2010} \\
GPRank & \cite{Silva2009} & \cite{Torkestani2012} \\  
GRankRLS & \cite{Pahikkala2010} & \cite{Pahikkala2010} \\
GroupCE & \cite{Lin2011} & \cite{Lin2011} \\ 
GroupMLE & \cite{Lin2010} & \cite{Lin2011} \\ 
IntervalRank & \cite{Moon2010} & \cite{Moon2010, Freno2011} \\
IPRank & \cite{Wang2009b} & \cite{Wang2009b, Torkestani2012} \\ 
KeepRank & \cite{Chen2009} & \cite{Chen2009} \\
KL-CRF & \cite{Volkovs2011} & \cite{Volkovs2011} \\ 
LAC-MR-OR & \cite{Veloso2008} & \cite{Veloso2008, Alcantara2010} \\ 
LambdaMART & \cite{Burges2010} & \cite{Asadi2013a, Ganjisaffar2011c} \\ 
LambdaNeuralRank & \cite{Papini2012} & \cite{Papini2012} \\ 
LambdaRank & \cite{Burges2006} & \cite{Papini2012, Tan2013} \\ 
LARF & \cite{Torkestani2012} & \cite{Torkestani2012} \\
Linear Regression & \cite{Cossock2006} & L3, \cite{Wang2012, Volkovs2011} \\
ListMLE & \cite{Xia2008} & \cite{Lin2010, Lin2011, Gao2014} \\
ListNet & \cite{Cao2007} & L2, L3, L4 \\
ListReg & \cite{Wu2011} & \cite{Wu2011}\\
LRUF & \cite{Torkestani2012b} & \cite{Torkestani2012b}\\
MCP & \cite{Laporte2013} & \cite{Laporte2013}\\
MHR & \cite{Qin2007} & L2\\
MultiStageBoost & \cite{Kao2013} & \cite{Kao2013}\\
NewLoss & \cite{Peng2010} & \cite{Peng2010}\\
OWPC & \cite{Usunier2009} & \cite{Usunier2009}\\
PERF-MAP & \cite{Pan2011} & \cite{Torkestani2012b}\\
PermuRank & \cite{Xu2008} & \cite{Xu2008}\\
Q.D.KNN & \cite{Geng2008} & \cite{Wang2013}\\
RandomForest & \cite{Gomes2013} & \cite{Gomes2013}\\
Rank-PMBGP & \cite{Sato2013} & \cite{Sato2013}\\
RankAggNDCG & \cite{Wang2013} & \cite{Wang2013}\\
RankBoost & \cite{Freund2003} & L2, L3, L4, \cite{Busa-Fekete2013, Alcantara2010, Sato2013}\\
RankBoost (Kernel-PCA) & \cite{Duh2008} & \cite{Duh2008, Sato2013}\\
RankBoost (SVD) & \cite{Lin2009} & \cite{Lin2009}\\
RankCSA & \cite{He2010} & \cite{He2010}\\
RankDE & \cite{Bollegala2011} & \cite{Sato2013}\\
RankELM (pairwise) & \cite{Zong2013} & \cite{Zong2013}\\
RankELM (pointwise) & \cite{Zong2013} & \cite{Zong2013}\\
RankMGP & \cite{Lin2012} & \cite{Lin2012}\\
RankNet & \cite{Burges2005} & \cite{Busa-Fekete2013, Papini2012, Niu2012}\\
RankRLS & \cite{Pahikkala2009} & \cite{Pahikkala2010}\\
RankSVM & \cite{Herbrich1999, Joachims2002} & L2, L3, \cite{Busa-Fekete2013, Freno2011, He2010, Alcantara2010, Papini2012}\\
RankSVM-Struct &  & L3, L4\\
RankSVM-Primal &  & L3, \cite{Lai2011}\\
RCP & \cite{Elsas2008} & \cite{Elsas2008}\\
RE-QR & \cite{Veloso2010} & \cite{Veloso2010}\\
REG-SHF-SDCG & \cite{Wu2009} & \cite{Wu2009}\\
Ridge Regression & \cite{Cossock2006} & L3\\
RSRank & \cite{Sun2009} & \cite{Lai2013}\\
SmoothGrad & \cite{Le2007} & \cite{Tan2013}\\
SmoothRank & \cite{Chapelle2010} & L3, \cite{Chapelle2010}\\
SoftRank & \cite{Taylor2008, Guiver2008} & \cite{Qin2010b}\\
SortNet & \cite{Rigutini2008} & \cite{Rigutini2008,Freno2011, Papini2012}\\
SparseRank & \cite{Lai2013b} & \cite{Lai2013b}\\
SVM$^{MAP}$ & \cite{Yue2007} & L3, \cite{Wang2012, Xu2008, Niu2012}\\
SwarmRank & \cite{Diaz-Aviles2009} & \cite{Sato2013}\\
TGRank & \cite{Lai2013} & \cite{Lai2013}\\
TM & \cite{Zhou2008} & \cite{Zhou2008, Papini2012, Tan2013}\\
VFLR & \cite{Cai2012} & \cite{Cai2012}\\
